A general model of microbial interactions in a chemostat

### 2019-12-17 tex/Tracking.tex
deleting parameter identification

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_difference_fit_5_LV}
	\caption{Difference between $u(t)$ and the $1+Ax(t)$, with $A$ shown in the right hand side of Figure \ref{Comparison Interaction Matrices}}
	\label{Difference fit}
\end{figure} 
\clearpage

@@

\begin{figure}[h]
	\centering	
\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\textwidth]{Synthetic_data_no_noise//Interactions_221119_no_noise_iter_5}
\end{subfigure}
\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
\label{Comparison Interaction Matrices}
\end{figure}

>>>>

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well. 
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
	\caption{Left: interactions of the synthetic data. Right: Interaction matrix obtained from solving problem \eqref{Parameter Identification}.}
	\label{Comparison Interaction Matrices}
\end{figure}

@@

\clearpage

@@
